Species motif participation provides unique information about species risk of extinction

### 2023-05-01 manuscript/JAE_reply.tex
old reply changes

            \textbf{R:} [[This one might be have to be Anna's task - I can't get the ggplot2 code to run.]]

>>>>

            \textbf{R:} We have reorganised the figure as suggested and, ourselves, now find it much clearer. We thank the Reviewer for the suggestion and hope that they also now find it easier to interpret. As an additional aid to understanding these results, we have added additional figures in the SI showing trends extracted from a model including proportion of motif, disturbance strength, network size, and connectance (across all networks within a size and connectance class). These can be compared with the peaks of the distributions of the within-network slopes to more easily understand how to these values relate to persistence.
